Staged Abstract Interpreters

### 2018-10-23 paper/10_intro.tex
update

1. we know how to stage an interpreter, intellectually it is natural to ask what would be an staged abstract interpreter,
and how to stage an abstract interpreter, given the structural similarity of interpreters and abstract interpreters. 
Futamura projection \cite{Futamura1999}

2. Multi-stage programming is widely used in high performance computation.
Precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bridging the gap between designing sound analyses and implementing efficient analyses.
partial evaluation on program analyzers is not a new idea, remove the interpretive overhead of repetively 
traversing the abstract syntax tree.
we revisit this approach from a more recent perspective by combining general abstract interpreters
and multi-stage programming.

@@

3. analyzing modern programs with large libraries are expensive, repetitively analyze the part of library,
modularity as in compilers, we need to a way to create summaries of libraries so that we can reuse them,
remove redundant analyzing of libraries.

>>>>

1. Futamura projection \cite{Futamura1999} shows that staging an interpreter yields a compiler.
literature on this approach, creating DSL.

Recent research uncovers a systematic approach to construct abstract interpreters from concrete interpreters.
Given the structural similarity between abstract and concrete interpreters, intellectually it is natural to 
wonder what would be a staged abstract interpreter, and how to stage an abstract interpreter 
having considered their functional dissimilarity.

2. Multi-stage programming is widely used in high performance computation.
Precise whole-program analysis can be very slow, how to optimize it systematically/mechanically?
bring existing high-performance computation facilities, in the form of meta-programming, into
semantic artifacts of abstract interpretation, i.e., abstract interpreters.
and bridging the gap between designing sound analyses and implementing efficient analyses.
without changing the abstract interpreter, just type

partial evaluation on program analyzers is not a new idea, remove the interpretive overhead of repetively 
traversing the abstract syntax tree.
we revisit this approach from a more recent perspective by combining general abstract interpreters
and multi-stage programming.

@@

3. analyzing modern programs with large libraries are expensive. 
why? 1. precise analysis usually required whole-program analysis; 2. to do wp analysis, need to 
repetitively analyze the parts of library.
As modularity in compilers, we need to a way to separately analyze programs, and create summaries of analyzed 
part so that we can reuse them, remove redundant analyzing of libraries.

### 2018-10-23 paper/abstract.tex
refactor AC 0CFA
update

In this paper, we study \textit{abstract} interpreters combined with multi-stage programming, i.e., the 
staged abstract interpreters. 
By staging an abstract interpreter respect to a program, we obtain a specialized analysis that runs faster.
By appying the idea to \textit{open} programs and considering the free variables as dynamic inputs, 
we obtain a modular analysis that generates sound partial analysis results which can be composed 
and reused later without losing precision, though the original abstract interpreter is a whole-program 
analysis algorithm.

@@

We also evaluate the improvement of performance on benchmark programs for a subset of Scheme.
The result shows ...

>>>>

In this paper, we study \textit{abstract} interpreters combined with multi-stage programming, i.e., the 
staged abstract interpreters. 
By staging the abstract interpreter with respect to a program, we obtain a specialized analysis that runs faster.
By appying the abstract interpreter with \textit{open} programs and considering the free variables as dynamic inputs, 
we obtain a modular analysis that generates sound partial analysis results which can be composed 
and reused later without losing precision, though the original abstract interpreter is a whole-program 
analysis algorithm.

@@

We also empirically evaluate the improvement of performance on benchmark programs for a subset of Scheme.
The result shows ...
